Carp\'{e} Data: Supporting Serendipitous Data Integration in Personal Information Management

### 2012-09-14 chi2012.tex
ps2 preogress

For each feed, 3-5 data records were obtained by querying the API directly for records of a that category's primary \emph{corresponding type}, listed in the second colum of Table \ref{tbl:prestudy2}. For example, while many of the APIs also provided access to other kinds of data, ranging from reviews to customer profilesonly product records were obtained for this category.  Once data records were obtained, simple complexity metrics were computed individually, followed by pairwise heterogeneity metrics.

@@

Heterogeneity was measured through \emph{pairwise consistency metrics} along the 
\begin{itemize}
\item \emph{Terminological consistency} - 
\item \emph{Structural consistency} - 
\item \emph{Semantic/Model consistency} - 
\end{itemize}

>>>>

For each feed, 3-5 data records were obtained by querying the API directly for records of a that category's primary \emph{corresponding type}, listed in the second colum of Table \ref{tbl:prestudy2}. For example, while many of the APIs also provided access to other kinds of data, such as customer reviews, only the primary type (product records) were obtained for the \emph{shopping} category.  Once data records were obtained, two complexity metrics were computed for each, followed by pairwise heterogeneity metrics.  Since, due to optional fields,  individual records could vary in the number of fields.  An alternative approach to using instance documents that we considered was to directly compare API schema definitions

@@

Heterogeneity was measured through \emph{pairwise consistency metrics} we derived from the 
\begin{itemize}
\item \emph{Terminological consistency} - 
\item \emph{Structural consistency} - 
\item \emph{Semantic/Model consistency} - 
\end{itemize}
